### 2024-03-18 Scripts/Manuscript/manuscript.Rmd
cleaned up manuscript, expanded readme file, and revised the data package desciptive information.

@@

Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@@

## Measurement Error

???connection/throughline of the measurement error hypotheses and other (including measurement error) hypotheses –\> is there a way to rewrite this part of the article to fit better as support/precedence to the QMP stuff???? –\> risky use of measurement!?!

As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the ??? supplementary materials.

@@

[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found under the supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.

@@

Relevant primary measures were identified by combing through the entirety of the methods section for each preregistered replication protocol. Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies. Descriptions of the extracted variables can be found in the sections below. The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the supplementary materials ???.

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure. Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych]. Default arguments were used for the function.

@@

Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were either altered from the coding key to better fit the QMP counting operationalization, all newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin, changes, and justifications can be found in supplementary materials ???.

@@

MOVE TO EXTERNAL SEARCH STRATEGY FILE: 
The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

These changes (to the QMP coding protocol) included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.

SUPPLEMENTARY MATERIALS ON ITEM REVISION AND ORIGIN:
Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to better fit the use of QMP ratios and associations between them and other coded aspects.

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

@@

If we look at the reliabilities obtained from the Many Labs responses on each measure for which scalar data could be accessed, the distributions of the Cronbach's alpha coefficients for each replication set for are displayed in Figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication. The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`

```{r Plot23AlphaCode,warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. ???Cronbach's alpha of the QMP items???

@@

# Changing rownames to reflect the variables
rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported psychometric evidence", "N modified", "Modified after/during data collection", "Total")

@@

## Risky Measurement Usage

??? Results based on calculated reliability are somewhat unstable, but we can definitely say that a large number of single item measures are used, not many multiple item measures are accompanied by a reported alpha coefficient, and when looking at the heterogeneity and selective reporting of alpha we see this...???

This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies. lllnot enough reliability coefficients were reported to conduct the planned analysis for hypothesis 1, and of the 77 measures only X measures in original articles and X in replication protocol reported any validity evidence. These findings show that reliability and validity evidence was similarly underreported in our sample, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].

The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies. Still, even for original articles a little over two-thirds of the multiple item measures were also reported without reliability evidence. ???Interestingly enough, when looking at the measures for which alpha could be calculated, alpha coefficients were reported only for those measures that were among the higher calculated mean alpha among the sample of measures for which alpha could be calculated as can be seen in figure \@ref(fig:Plot23AlphaCode)???

This only covers part of the spectrum of the measures found in the sample, across both original and replication studies, less than half of the coded measures were multiple item scales. Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement. The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement], ???and reliability risks???. This is particularly concerning given that the analyses of the calculated reliabilities of the multiple item measures showed that some measures ???EXPLORATORY ANALYSIS IDEA: relation of the calculated reliabilities and N items of the measure???, and exploratory analyses of the multiple item measure replication datas, for which unidimensionality could be tested, showed only little support for unidimensionality (see Appendix A as was also observed by @shaw2020measurement).

???APPENDIX with SENSITIVITY ANALYSES/UNIDIMIMENSIONALITY ANALYSIS???: This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications. While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure. For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc]. However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this study were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2. To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.]]]

Several results did show more promising findings for the way measurement related issues are treated in replications. Firstly, the support found for hypothesis 2 provided some evidence showing that most of the variability in reliability coefficients is between measures, rather than within measures across different locations. This would be a prerequisite showing that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable. However, the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain. Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials. Still, in most instances neither original nor replication provided information on the exact version of their measure. This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves. Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4. This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.

@@

While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed. The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect. On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects. Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level. This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test ???logic/cited work???.

[[[??? reliability meta-analysis???

@@

The effect of QMPs on replicability can additionally be traced back to the effect of original article QMPs on replication QMPs. The test for hypothesis 6 showed that, in line with expectations, there was a positive association between the total QMPs of an original study and the total QMPs in the protocol of the replication for that study. The idea here is that when information on or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure. As a result, both the underreporting of measurement details and use of unverified measurements may persist. [make the domino effect more clear/better written here]

Furthermore, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally. As a result, the relation between the original and replication studies weakens, lowering the chances that similar results will be found, and possibly even invalidating the replication's relation to the original study as a replication [@flake2022construct].

However, it is worth noting that hese relations were only found for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D). The initial protocol was revised because the ratings based on that protocol were considered to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered. This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree. As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol. With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference. It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication. In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.

@@

The design of this study came with certain limitations. First of all, there was no (quasi-)experimental manipulation included of the quality or reporting practices of the measures. As a result, the ability to investigate the exact causal links between QMPs and replicability was limited. Secondly, alternative ways to analyse the data could have been used, or certain parts of the data could have been examined more closely. Several methodologies for doing so have already been suggested throughout the article such as ???insert methodology here???, and others are presented in the appendix ???sensitvity and exploratory analysis appendix???. Future research can use this study as a basis to find relevant data sources and methodologies to use in order to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.

It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs. Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols. Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else. This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details. However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs. This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data. \<-- try to collpase with previous paragraph???

Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used. The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results. Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed. As a first step, the coding protocol from this study and the coding key from @flake2022construct can be used as a basis. \<- importance ???

As a last note on QMPs, it is worth highlighting the way the QMP ratios were calculated. The total QMP ratio was based on the counts for each of the items from all the different QMP types divided by the total number of applicable questions. However, for each QMP type the number of items was different. This means that QMP types with a larger number of items (such as operationalisation) had a greater impact on the total QMP ratio than QMP types with a smaller number of items (such as definition). If the impact for each QMP type on each other and replicability is considered equally important, the total QMP ratio may not be considered a valid indice. On the other hand, it could be that each item should be considered equally important rather than each QMP type. For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight. However, this is an assumption this study cannot provide evidence for. [Focus more on the fact that there is a mixture in the QMP ratio’s: which influences the relations perhaps like ...]

The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses. While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.

Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study. Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition. However, future research might consider methods specifically designed to assess reliability and validity of single item measures. This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).

Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures. Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations. This can be done through measurement invariance testing. Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item]. @shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2. Investigations similar to this have also been suggested for future replication projects [@flake2022construct]. For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs. \<-- also include other suggestions like for paragraph 1 of this section???

@@

Taking all the findings together, the following assessments will be relevant to consider for future replication research. With respect to the quality of measurement reporting, the small number of reported reliabilities, small number of reported psychometric validity evidence, and lack of unidimensionality evidence for data aggregated to a single indicator corroborate findings by @shaw2020measurement & @flake2022construct. Evidence supporting the measures used in replication should be reported more frequently, so that they can be evaluated and the validity of replication research can be improved.

>>>>

appendix:
  - "Scripts/AppendixScripts/Appendix_pre-reg_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_multilevel_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_omega_analyses.Rmd"
  - "Scripts/AppendixScripts/Appendix_initial_QMP_analyses.Rmd"

@@

Measurement in psychological science is defined in large part by one overarching issue: the psychological constructs of interest, such as affective state and intelligence, cannot be measured directly [@flake2017construct]. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@@

## Measurement Error
As a first step the state of measurement error in original and replication research in psychology is investigated, to assess the scope of @stanley2014expectations's findings in practice:

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the data_search_details.pdf supplementary materials.

@@

[^2]: The steps taken to access the replication protocol data from Many Labs 5 were not preregistered, and only became clear upon further investigation of the accessible information. The specific names and locations of the files that were used as the datasets can be found in the data_search_details.pdf supplementary materials of the OSF page of this article <https://osf.io/gft46/%7D>.

@@

Relevant primary measures were identified by combing through the entirety of the methods section for each preregistered replication protocol. Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies. Descriptions of the extracted variables can be found in the sections below. The coding protocol and explanations on how the articles and replication protocols were searched through to answer the questions in the coding protocol can be found in the coding protocols folder of the supplementary materials.

@@

Cronbach's alpha was calculated as the main score reliability index used in the analyses, as remains the most commonly used indicator of the reliability of a measure [@flake2017construct]. Cronbach's alpha was calculated using the alpha function from the psych R package [@R-psych]. Default arguments were used for the function.

@@

Beside these quantitative variables, a total of four qualitative variables were also included to provide more detailed information on some aspects of the measure and its reporting. Details on the items used, their origin, changes, and justifications can be found in the coding protocol information supplementary materials.

@@

@@

Despite the lack of reliability reporting,if scalar data could be accessed for a measure the reliability could be calculated for each lab it was used in. The distributions of the Cronbach's alpha coefficients for each replication set are displayed in figure \@ref(fig:Plot23AlphaCode), separated by successful and unsuccessful replication. The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`.

When comparing the reported reliabilities with the calculated reliabilities displayed in figure \@ref(fig:Plot23AlphaCode), all but `r apa_num(sum(plot_23_data_reported_alpha$coefficient_difference > 0), numerals = FALSE)` of the reported reliabilities are in the lower half of the distribution of the calculated reliabilities within their own measure. However when looking across the measures, the mean of the distribution of the calculated coefficients of all but `r apa_num(sum(aggregate(plot_23_data_alpha_reordered$alpha, list(plot_23_data_alpha_reordered$g), FUN = mean)[plot_23_data_reported_alpha$article_order,2] <= mean(data_h3_multiple$alpha)), numerals = FALSE)` of the measures that have reported reliability coefficients is larger than the mean calculated Cronbach's alpha.

```{r Plot23AlphaCode, warning = FALSE,  fig.cap = "Distributions of calculated Cronbach’s alpha coefficients (> 0) calculated for the responses on a measure at each lab location, across the eighteen distinct measures for which suitable raw data was available to calculate Cronbach’s alpha coefficients from. The green lines indicate the meta-analytic prediction interval lower and upper bound. The blue triangles indicate the reported alpha coefficient for that measure from the original article, when available. The Tau column besides the figure shows the tau heterogeneity estimate based on a meta-analysis of the calculated reliabilities for each measure, meta-analysis for which the Q-test for Heterogeneity was signicant at alpha < .05 are in black, not significant results are left grey. The Diff column shows the difference between reported reliability and the average reliability calculated from the Many Labs data for the applicable measures, the differences in bold are for reported reliabilities that fell outside the 95% quantile of calculated reliability scores."}

@@

In order to visualize the results on QMPs, the proportions of the QMP ratio obtained for each QMP type (see Table \@ref(tab:QMPCodingInfoTable)) are shown across the top layer of Figure \@ref(fig:Plot456Code) for both replication protocols and original articles. While in the bottom layer of Figure \@ref(fig:Plot456Code) the overlayed distributions of the total QMP ratios from the replication protocols and original studies are displaued, with dots indicating each datapoint, and the line indicating the mean for either distribution. A large number of QMP ratios are missing for the QMP modification type , because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified.

@@

# Changing rownames to reflect the variables
rownames(reporting_descriptives_table) <- c("Specified measure version", "Used existing materials", "Specified being newly created", "Reported validity evidence", "N modified", "Modified after/during data collection", "Total")

@@

## Risky Measurement Usage
This study assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects, and the original articles they attempted to replicate. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that validity evidence and reliability coefficient reporting for measures was lacking in replications and original studies. This is illustrated in our sample by the fact that reliability coefficients were reported in too small quantity to conduct the planned analysis for hypothesis 1, and because of the `r nrow(coded_data_replications)` measures only `r sum(coded_data_original_shortened$sel_psychometric_evidence_REV != "None" & coded_data_original_shortened$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` measures in original articles and `r sum(coded_data_replications$sel_psychometric_evidence_REV != "None" & coded_data_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)")` in replication protocol reported any validity evidence. Thus, reliability and validity evidence was underreported in our sample similarly to the findings of @shaw2020measurement, @flake2017construct & @flake2022construct, a problem that has also been addressed in earlier literature on this topic [@vacha1999practices; @green2011recent].

The adjusted test for hypothesis 1, while not able to test differences in actual coefficient values, did show contradictory to hypothesis 1 and similarly to @flake2022construct, that original articles reported reliability coefficients more often than replication studies. Still, even for original articles `r round(100 * (table(coded_data_original_shortened$N_items)[["multiple item measure"]] - sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)])) / table(coded_data_original_shortened$N_items)[["multiple item measure"]], digits = 0)`% of the multiple item measures were also reported without reliability evidence.

This only covers part of the spectrum of the measures found in the sample, across both original and replication studies, less than half of the coded measures were multiple item scales. Research commonly made use of single item measures (see Figure \@ref(fig:ReliabilityReportingFlowDiagram) for more details), an observation that was also made by @shaw2020measurement. The use of single item measures comes with many risks with regard to validity [@diamantopoulos2012GuidelinesChoosingMultiItem; @nunnallyOverviewPsychologicalMeasurement1978]. Additionaly, by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement]. This is particularly concerning given that the exploratory unidimensionality tests for the multiple item measures (appendix A) revealed that only `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of the `r nrow(cfa_results)` relevant measures satisfied the conditions for unidemensionality. Thus showing little support for unidimensionality of measurement in general, although the result from this analysis is tentative on several assumptions (see Appendix A).

Several results did show more promising findings for the way measurement related issues are treated in replications at least. Firstly, the pre-registered test for hypothesis 2 showed that most of the variability in reliability coefficients in the sample is between measures, rather than within measures across different locations. Additionally, the meta-analysis of Cronbach's alpha showed non-significant and small heterogeneity estimates for most of the measures analysed. This is a prerequisite showing that measurement generally operated similarly across locations, which would make the scores from the different lab locations directly comparable and aggregatable. However, the small sample number of measures for which reliability could be assessed does mean that the generalisability remains uncertain. Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials. Still, in most instances neither original nor replication provided information on the exact version of their measure. This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves. Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4. This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.

@@

While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed. The number of measures for which reliability was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$alpha)), numerals = FALSE)`), it could be that the test was simply underpowered to detect the effect. On the other hand, it might be the result of measurement error's tendency to reduce heterogeneity in estimates of the same effect, making the observed effects more similar [@olsson-collentine2023UnreliableHeterogeneityHow]. This may have resulted in effects that appeared to homogeneously show evidence in one direction, which may explain the differences in conclusions observed between this article and the simulation studies of @stanley2014expectations.

@@

The effect of QMPs on replicability can additionally be traced back to the effect of original article QMPs on replication QMPs. The test for hypothesis 6 showed that, in line with expectations, there was a positive association between the total QMPs of an original study and the total QMPs in the protocol of the replication for that study.

The idea here is that when information on or support for the use of a measurement is lacking, any subsequent replication attempt is expected to also lack information on the measure. As a result, both the underreporting of measurement details and use of unverified measurements may persist in the replication. Consequently, ensuring that the original measurement is mimicked becomes difficult to verify when the measurement was not documented well originally. In turn, the relation between the original and replication studies may weaken [@flake2022construct], and as a result, constructs are measured substantially differently, thus the subsequent test in the replication is substantially different from the test in the original article. This would mean that the observed effects in the replication may differ from the original not only due to sampling error, but also due to true differences in the assessed effect as the result of the measurement used.

However, it is worth noting that these relations were only found for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see Appendix D). The initial protocol was revised because the ratings based on that protocol were considered to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered. This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree. As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol. With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference. It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication. In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.

@@

The design of this study came with certain limitations. First of all, there was no (quasi-)experimental manipulation included of the quality or reporting practices of the measures. As a result, the ability to investigate the exact causal links between QMPs and replicability was limited. Secondly, alternative ways to analyse or expand the sample could have been used. The coding protocol was changed within the scope of this study, which illustrates that there was no validated methodology for analyzing the data, and there is no prior evidence validating the use of QMP ratios to represent questionable measurement practices. Future research can use this study as a basis to find relevant data sources, and develop methodologies that can be used to compliment and extend the findings of this study, or test causal links between measurement usage and replicability.

It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs. Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols. Regardless, this study assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else. This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details. However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs. This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.

As a final note on QMPs, it is worth highlighting a specific aspect about the way the QMP ratios were calculated. This relates to the fact that non-applicable items, while adjusted for by coding those items as 0 in both the numerator and denominator of the QMP ratio calculation, could exert a strong influence on the value of the QMP ratio. For example, for one measure all relevant information regarding the measure was reported, for another no information was provided on the measure at all and the items were all non-applicable. In both cases the QMP ratio would be 0, however we would not consider the latter case to be nearly as informative as the first. As a result the relation between QMP ratio and measurement reporting quality is obscured. There is no simple solution to this problem based on teh current data, however future research may wish to include qualitative analyses of the informativeness of measurement detail reporting to provide a more thorough and complete picture.

The small sample of measures for which reliability coefficients could be assessed limited the degree to which substantial interpretations can be made from the reliability analyses. While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this study mostly ignored in the analyses of reliability and validity: single-item measures.

Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this study. However, future research might consider methods specifically designed to assess the reliability of single item measures. This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this study (see Figure \@ref(fig:ReliabilityReportingFlowDiagram)).

Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures. Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations. This can be done through measurement invariance testing. Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item]. @shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2. Investigations similar to this have also been suggested for future replication projects [@flake2022construct]. For these reasons, future research should consider using measurement invariance tests, when assessing measurement consistency in replications across different labs.

@@

Taking all the findings together, the following assessments will be relevant to consider for future replication research. With respect to the quality of measurement reporting, the small number of reported reliabilities, and lack of reported validity evidence corroborate findings by @shaw2020measurement & @flake2022construct. Evidence on the reliability and validity of the measures used in both replication and original research should be reported more frequently, so that measures can be evaluated and the validity of replication research can be improved.

The results suggest that the use of structured measurement reporting protocols may be an effective way of reducing QMPs, and may explain why the replication protocols had on average lower QMPs than original articles in this study. However, the reliability and validity evidence reporting rate was lower in the Many Labs replication protocols that made use of structured reporting protocols compared to original articles. These protocols could therefore still increase the attention they give to reporting reliability and validity evidence.

Furthermore, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications. This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity. In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure. The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessing]. Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate.

In case the quality appears low, replication attempts can still proceed with some adjustments. One option is to change the focus of the replication to be conceptual rather than direct. In that case the measure and the operationalisation can be freely altered from the original, which means that a more sufficient test of the theory can be developed. If deemed necessary, a direct replication can always be performed later based on the conceptual replication. In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.
